---
title: "RMarkdown Demonstration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      error = FALSE, fig.width = 10)
```

## Intital Package Installations

First, you will need to install some packages:

```{r, eval = FALSE}
packs = c("tidyverse", "data.table", "DT", 
          "plotly", "ggplot2", "corrplot", 
          "stargazer", "knitr", "rmarkdown")

install.packages(packs)
```

You will only need to install them once, so do not worry about running this after you do it the first time.

## Our Data

We are going to make it easy on ourselves and use some of the data that R has built into it.  We are going use the "diamonds" data from the ggplot2 package.

```{r}
library(ggplot2)
```


## Data Exploration

Data exploration is an important part of the statistical programming process.  We can start by taking a peak at our actual data.  This could also be helpful for people who may want to take a look at our document.

```{r}
DT::datatable(diamonds)
```


We often like to take an initial look at the correlations within our data.  This can be most enlightening, but dealing with a massive correlation matrix can be a hassle.  Instead, we can go the visual route. Before we produce our visualization, we need to do a little data work. The diamonds data contains a few variables that would need some work before being thrown into a correlation matrix. We will, instead, just work with the purely numeric variables.

```{r}
library(dplyr); library(corrplot)

diamonds %>% 
  select(price, carat, depth, table, x, y, z) %>% 
  cor() %>% 
  corrplot.mixed()
```


## Data Visualization

### Static

Often times, we might just want a nice static visualization.  Static, however, does not mean simple. R gives us the ability to create layers within our visualizations.  Likely the most popular package for static visualizations is ggplot2.



```{r}
library(ggplot2)

p = ggplot(diamonds, aes(carat, price, color = cut)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  facet_wrap(~ color) +
  theme_minimal()

p
```

### Interactive 

There are a wide variety of packages designed for interactive visualizations in R. We already saw a few of the htmlwidget packages in use. Since we already have a ggplot created, we can just throw it to the ggplotly function from the plotly package.

```{r}
library(plotly)

ggplotly(p)
```


## Results

We can do a lot of different things with our results.  For example, we might want some of our results to actually be within our text -- there exists a significant relationship between carats and price (*r* = `r round(cor(diamonds$carat, diamonds$price), 2)`).

We might want to include some more expanded results. 

The following is our standard regression output, but in a nice interactive table:

```{r}
testLM = lm(price ~ carat, data = diamonds)

DT::datatable(broom::tidy(testLM))
```

We might also want some model comparisons:

```{r, results = "asis"}
testLM2 = lm(price ~ carat + depth, data = diamonds)

stargazer::stargazer(testLM, testLM2, type = "html", header = FALSE)
```

